\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{simplewick}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}

\usepackage{tikz-cd}

%%%%%%%%%%% Box pacakges and definitions %%%%%%%%%%%%%%
\usepackage[most]{tcolorbox}
\usepackage{xcolor}
\usepackage{dashrule}
\usepackage{mathtools}


% Define the colors
\definecolor{boxheader}{RGB}{0, 51, 102}  % Dark blue
\definecolor{boxfill}{RGB}{173, 216, 230}  % Light blue

% Define the tcolorbox environment
\newtcolorbox{mathdefinitionbox}[2][]{%
    colback=boxfill,   % Background color
    colframe=boxheader, % Border color
    fonttitle=\bfseries, % Bold title
    coltitle=white,     % Title text color
    title={#2},         % Title text
    enhanced,           % Enable advanced features
    attach boxed title to top left={yshift=-\tcboxedtitleheight/2}, % Center title
    boxrule=0.5mm,      % Border width
    sharp corners,      % Sharp corners for the box
    #1                  % Additional options
}
%%%%%%%%%%%%%%%%%%%%%%%%%

\newtcolorbox{dottedbox}[1][]{%
    colback=white,    % Background color
    colframe=white,    % Border color (to be overridden by dashrule)
    sharp corners,     % Sharp corners for the box
    boxrule=0pt,       % No actual border, as it will be drawn with dashrule
    boxsep=5pt,        % Padding inside the box
    enhanced,          % Enable advanced features
    overlay={\draw[dashed, thin, black, dash pattern=on \pgflinewidth off \pgflinewidth, line cap=rect] (frame.south west) rectangle (frame.north east);}, % Dotted line
    #1                 % Additional options
}
\usepackage{biblatex}
\addbibresource{sample.bib}


%%%%%%%%%%% New Commands %%%%%%%%%%%%%%
\newcommand{\T}{\mathcal T}
\newcommand{\cl}{\text cl}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cZ}{\mathcal{Z}}


\newcommand{\defeq}{\vcentcolon=}
\newcommand{\eqdef}{=\vcentcolon}
\newcommand{\ket}[1]{|#1 \rangle}
\newcommand{\bra}[1]{\langle #1|}
\newcommand{\mean}[1]{\left\langle #1 \right\rangle}
\newcommand{\inner}[2]{\langle #1 | #2 \rangle}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Hilbert}{\mathcal{H}}
\newcommand{\oper}{\hat{\Omega}}
\newcommand{\lam}{\hat{\Lambda}}
\newcommand{\qedsymbol}{\hfill\blacksquare}

\newcommand{\bigslant}[2]{{\raisebox{.2em}{$#1$}\left/\raisebox{-.2em}{$#2$}\right.}}
\newcommand{\restr}[2]{{% we make the whole thing an ordinary symbol
  \left.\kern-\nulldelimiterspace % automatically resize the bar with \right
  #1 % the function
  \vphantom{\big|} % pretend it's a little taller at normal size
  \right|_{#2} % this is the delimiter
  }}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\tcbset{theostyle/.style={
    enhanced,
    sharp corners,
    attach boxed title to top left={
      xshift=-1mm,
      yshift=-4mm,
      yshifttext=-1mm
    },
    top=1.5ex,
    colback=white,
    colframe=blue!75!black,
    fonttitle=\bfseries,
    boxed title style={
      sharp corners,
    size=small,
    colback=blue!75!black,
    colframe=blue!75!black,
  } 
}}

\newtcbtheorem[number within=section]{Theorem}{Theorem}{%
  theostyle
}{thm}

\newtcbtheorem[number within=section]{Definition}{Definition}{%
  theostyle
}{def}



\title{Feynman Diagrams \& QFT Notes}
\author{Keshav Balwant Deoskar}

\begin{document}
\maketitle

% \vskip 0.5cm
These are notes taken from lectures on Feynman Diagrams and QFT delivered by Ivan Burbano. Any errors that may have crept in are solely my fault.
% \pagebreak 

\tableofcontents

\pagebreak

\section{January 26 - First meeting! Setting goals.}


\vskip 1cm
\subsection{The goal}
This course wll be a very first-principles, barebones experience. Our goal for the next month will be to develop the tools to solve the integral

\[ \int_{-\infty}^{\infty} dx \; e^{-S(x)} O(x)\]

where $S(x) = \frac{1}{2}ax^2 + \frac{1}{3!} gx^3 + \frac{1}{4!}\lambda x^2 + \cdots$, the constants $a, g, \lambda$ etc. must be positive reals and are called \emph{coupling constants} and $O(x)$ is a polynomial in $x$. 

\vskip 1cm
\subsection*{What is the physical motvation for this integral?}

There are \emph{two} sides to the physics related to this integral: Quantum (this is what we want!) and Statistical (this is what we do!).
\vskip 1cm

[Insert picture]

\vskip 0.5cm
\subsection{The Quantum regime}
In the Quantum regime, \emph{fields} become \emph{fuzzy!} We can't quite pin down what the configuration of the field is, rather we can tell what the \emph{probability amplitude} of any given field configuration will be at a point in (space)time.

\vskip 0.5cm
So, the fundamental question in QM is: 

\begin{dottedbox}
  If at time $t_i$ we prepare a field $\phi_i$, what is the probability amplitude that, at $t_f$, I measure $\phi_f$?
\end{dottedbox}

We can say that 
\[ \phi_f = \inner{\phi_f}{U(t_f, t_i)| \phi_i} \]
where $U(t_f, t_i)$ is called the \emph{propagator} or the \emph{time-evolution operator.}

% \vskip 0.5cm

According to feynman, the answer can be found by integrating the \emph{action} over the space of all field configurations.



i.e.
\[ = \int \mathcal{D}\Phi e^{i S(\Phi)} \]
where we are integrating over all field configurations $\Phi(x)$ such that $\Phi = \phi_i$ at $t_i$ and $\Phi = \phi_f$ at $t_f$.



In more formal notation, the set over which we are integrating is
\[ \{ \phi \in C^{\infty}([t_i, t_f] \times \Sigma) \;\;:\;\; \restr{\phi}{\Sigma_i} = \phi_i; \restr{\phi}{\Sigma_f} = \phi_f \} \] where $\Sigma$ denoted the space we're working on.


\vskip 0.5cm
\subsection{The Statistical Side of Things}
This is what we actually do! 

\vskip 0.5cm
Suppose we have some region, say a table, $T$ populated by some \emph{field} $\phi(x)$. For instance, it could be some spin distrbiution i.e. the field assigns each point on the table $T$ with some spin.

\vskip 0.5cm
Boltzmann showed that the probability (\emph{not} probability amplitude) for the field to be in configuration $\phi$ is proportional to 
\[ e^{-S(\phi)} \]
where $S(\phi)$ is the energy of the field configuration.

\vskip 0.5cm
In particular, the probablity is 
\[ \frac{e^{-S(\phi)}}{\mathcal{Z}} \]

where 
\[ \mathcal{Z} = \int \mathcal{D}\phi e^{-S(\phi)} \]
is the integral over the space (of all field configurations) of probabilities. It's called the \textbf{Partition Function}.

\vskip 0.5cm
\begin{dottedbox}
  Quick aside, what about dimensions? 

  \vskip 0.5cm
  The partition function is dimensionless, whereas the feynman path integral we covered in the Quantum Regime \emph{is} dimension-ful. This is our first hint that something is amiss with the path-integral. (Has to do with renomalization).
\end{dottedbox}

\vskip 0.5cm
\begin{dottedbox}
  Note: The ket $\ket{x}$ \emph{does have units}. In particular, the completeness relation tells us 
  \[ \int dx\; \ket{x} \bra{x} = 1\] 
  So, $\ket{x}$ has units of $\frac{1}{\sqrt{\text{Length}}}$
\end{dottedbox}

\subsection{An example from Stat. Mech: Kinetic Theory of gasses}

\vskip 0.5cm
Now, let's actually solve an integral! Let's compute 
\[ \int_{-\infty}^{\infty} d\phi e^{-S(\phi)} O(\phi) \]

where 
\[ S(\phi) = \frac{1}{2} \phi m^2 \phi - \frac{g}{3!} \phi^3 -  \frac{\lambda}{4!}  \phi^4 \] where $m^2 > 0$.

\begin{enumerate}
  \item Partition Function : $O = 1$
  For a \underline{free theory}, we have $g = \lambda = \cdots = 0$
\end{enumerate}

So, our integral turns into 

\[ \boxed{\int_{-\infty}^{\infty} d\phi e^{-\frac{1}{2}m^2 \phi^2}} \]

This integral is intimately connected to the Kinetic Theory of Gasses.

\underline{\textbf{Sol:}}

\begin{align*}
  \int_{-\infty}^{\infty} d\phi e^{-\frac{1}{2}m^2 \phi^2} &= \sqrt{\left( \int_{-\infty}^{\infty} d\phi e^{-\frac{1}{2}m^2 \phi^2} \right)^2} \\
  &= \sqrt{\int_{-\infty}^{\infty} d\phi e^{-\frac{1}{2}m^2 \phi^2} \int_{-\infty}^{\infty} d\psi e^{-\frac{1}{2}m^2 \phi^2}} \\
  &= \sqrt{\int_{\R^2} \;d\phi d\psi\; e^{-\frac{1}{2}m^2(\phi^2 + \psi^2)}} 
\end{align*}

Now, we convert to polar coordinates with $r^2 = \psi^2 + \phi^2$, $u = \frac{1}{2}r^2 m^2$, $du = dr r$

\begin{align*}
  &= \sqrt{\int_{\R^2} \;\underbrace{d\phi d\psi}_{=r dr d\theta}\; e^{-\frac{1}{2}m^2(\phi^2 + \psi^2)}} \\
  &= \sqrt{2\pi \int_0^{\infty} \;dr\;r\;e^{-\frac{1}{2} r^2 m^2 } } \\
  &= \sqrt{\frac{2\pi}{m^2}} \int_0^{\infty} du\;e^{-u} \\
  &= \sqrt{\frac{2\pi}{m^2}}
\end{align*}

\vskip 0.5cm
\begin{dottedbox}
  \underline{Exercises!}

  \vskip 0.5cm
  \begin{enumerate}
    \item \[ \int_{-\infty}^{\infty} d\phi e^{-\frac{1}{2}m^2 \phi^2 + J\phi} \]
    \item \[ \int_{-\infty}^{\infty} d\phi_1 d\phi_2 e^{-\frac{1}{2} \vec{\phi^T} \cdot A \vec{\phi} } \]
    where $A$ is any symmetric $2 \times 2$ matrix (can generalize to $n \times n$ matrices!).
  \end{enumerate}
\end{dottedbox}


\pagebreak
\section{February 2 - } 

\subsection{Last time}
\begin{itemize}
  \item We computed the integral ($m^2 > 0$)
  \[ \mathcal{Z} = \int_{-\infty}^{\infty} d\phi e^{\phi m^2 \phi} = \sqrt{\frac{2\pi}{m^2}} \]
  \item We called this integral the \emph{\textbf{partition function of our free theory}} (the "free" tells us that the action $S(\phi) = \frac{1}{2}\phi m^2 \phi$ is quadratic).
\end{itemize}

\vskip 1cm
\subsection{Today}
\begin{itemize}
  \item If we have a polynomial $\mathcal{O}(\phi)$, we want to calculate the expectation value 
  \[ \langle \mathcal{O} \rangle \defeq \frac{1}{\mathcal{Z}}\int_{-\infty}^{\infty} d\phi e^{-\frac{1}{2}\phi m^2 \phi} \mathcal{O}(\phi) \]
\end{itemize}

\vskip 1cm
\subsection{Schwinger-Dyson equation}

Consider the following where $S(\phi)$ and $\mathcal{O}(\phi)$ are just some polunomails and $S(\phi) \rightarrow \infty$ as $\phi \rightarrow \pm \infty$

\vskip 0.5cm
\begin{mathdefinitionbox}{Theorem (Version 1)}
  \[ \int_{-\infty}^{\infty} d\phi e^{-S(\phi)} \frac{d\mathcal{O}}{d\phi} = \int_{-\infty}^{\infty} d\phi e^{-S(\phi)}\frac{dS}{d\phi} \mathcal{O} \]
\end{mathdefinitionbox}

\vskip 0.5cm
We can divide both integrals by $\mathcal{Z}$ to obtain the other form of the theorem:

\vskip 0.5cm
\begin{mathdefinitionbox}{Theorem (Version 2)}
  \[ \mean{\frac{d\mathcal{O}}{d\phi}} = \mean{\frac{dS}{d\phi} \mathcal{O}} \]
\end{mathdefinitionbox}

\vskip 0.5cm
\underline{Proof:}
\vskip 0.5cm

\begin{align*}
  \int_{\infty}^{\infty} d\phi \frac{d}{d\phi} \left( e^{-S(\phi)} \mathcal{O}(\phi) \right) &= \left[ e^{-S(\phi)} \mathcal{O}(\phi) \right]_{-\infty}^{\infty} = 0
\end{align*}

\vskip 0.5cm
Now, why is this useful? Our whole goal today was to compute Expectation values but we haven't been calculating a whole lot of them.

\vskip 0.5cm
Well, notice the following:
\begin{itemize}
  \item $\mean{1} = 1$
  \item deg$\frac{d\mathcal{O}}{d\phi} =$ deg$\mathcal{O}$ - 1
  \item deg$\left(\frac{dS}{d\phi} \cdot \mathcal{O}\right) = $ deg $S$ + deg$\mathcal{O}$ - 1
\end{itemize}

\vskip 0.5cms
By proving the Schwniger-Dyson equation, we've gotten a relation between something of higher of degree and something of lower degree. So, we can go recursively until we reach a polynomial of degree $1$, whose expectation value will be piss easy to calculate since $\mean{1} = 1$.

\vskip 0.5cm
\begin{dottedbox}
  Also, quick side note, $\frac{dS}{d\phi}$ give us the \emph{\textbf{Lagrange Equations}}, and so are called the \emph{\textbf{Equations of motion!}}
\end{dottedbox}

\vskip 0.5cm
\underline{Note}: We call anything that's a function of $\phi$ an operator. We'll relate this to the more familiar notion of an operator in Quantum Mechanics later.

\vskip 1cm
\subsection{Returning to our Free Theory}
\vskip 0.5cm
Now, returning to our free theory with action $S(\phi) = \frac{1}{2}\phi m^2 \phi$ (Equations of motion $\frac{dS}{d\phi} = m^2 \phi$). To caluclate the expectation value  $\mean{\phi^2}$ we express it as 
\begin{align*}
  \mean{\phi^2} &= \frac{1}{m^2} \mean{\underbrace{m^2 \phi}_{dS/d\phi} \underbrace{\phi}_{\mathcal{O}}} \\
  &= \frac{1}{m^2} \mean{ \frac{dS}{d\phi} \mathcal{O}}
\end{align*}

Then, applying the Schwinger-Dyson Equation, we get 
\begin{align*}
  \mean{\phi^2} &= \underbrace{\frac{1}{m^2}}_{\mean{\phi \phi}} \mean{\frac{d\phi}{d\phi}} = \frac{1}{m^2}
\end{align*}
This term $1/m^2$ is "contracted" from the $\mean{\phi \phi}$ term, and is called the \emph{\textbf{propagator}}.

\vskip 1cm
\subsection{$\phi^4$ Free Theory}

Let's now do something similar for $\phi^4$.

\begin{align*}
  \mean{\phi^4} &= \frac{1}{m^2} \mean{m^2 \phi \; \phi^3} \\
  &= \frac{1}{m^2} \mean{\underbrace{\frac{d}{d\phi}(\phi^3)}_{\frac{d}{d\phi}(\phi \phi \phi)}} \text{  (By Schwinger-Dyson)} \\
  &= \frac{1}{m^2} \mean{\frac{d\phi}{d\phi} \phi \phi} + \frac{1}{m^2} \mean{\phi \frac{d\phi}{d\phi} \phi}  +\frac{1}{m^2} \mean{\phi \phi\frac{d\phi}{d\phi}} \\
  &= \mean{\phi \phi \phi} + \mean{\phi \phi \phi} + \mean{\phi \phi \phi} \\
  &= [\text{Draw feynman diagrams}]
\end{align*}


[WATCH RECORDING AND ADD THE FEYNMAN DIAGRAM REPRESENTATIONS OF THESE TERMS -- IMPORTANT
\begin{itemize}
  \item Every $\phi$ is a dot with a line coming out of It
  \item When we contract two $\phi$'s we connect their lines
\end{itemize}
]

\vskip 0.5cm
\begin{dottedbox}
  \underline{Exercises:}
  \begin{enumerate}
    \item Show that 
    \[ \mean{\phi^4} = \frac{(n - 1)!!}{m^n} \] where the double exclaimation is the double-factorial.

  \vskip 0.5cm
  \item Write the diagrams for $\mean{\phi^6}$ in a few dfferent ways:
  \item \begin{align*}
    \mean{\phi^6} &= \mean{\phi \phi \phi \phi \phi \phi} \\
    &= \mean{\phi^2 \phi^4} \\
    &= \mean{\phi^3 \phi^3} \\
    &= \mean{(\phi^6) \phi^0}
  \end{align*}

  \vskip 0.5cm
  \item Compute the partition function
  \[ \mathcal{Z} = \frac{1}{h} \int_0^{L} \mathrm{d}x \int_{-\infty}^{\infty} \mathrm{d}p\;e^{-\frac{-\beta p^2}{2m}} \]
  explicitly (\emph{Hint: Convert into the same form as we've solved in class using the substitution $\phi = \frac{Lp}{h}$ and then figure out what the action $S(\phi)$ should be.})

  \item Also Compute the free Energy $F$, where $e^{-\beta F} = \mathcal{Z}$.
  \begin{itemize}
    \item Note that $F =  E - TS, dF = -S dT - pdV$
    \item $p = -\left( \frac{\partial F}{\partial V} \right)_{\beta} \implies$ Ideal Gas Law
  \end{itemize}
  \end{enumerate}
\end{dottedbox}

\pagebreak

\section{February 9 - Wick's Theorem and Interacting Partition Functions}

\subsection*{Recap}
So far, we've
\begin{itemize}
  \item Introduced the partition Function
  \[ \cZ = \int_{\infty}^{\infty} \mathrm{d} \phi e^{-S(\phi)} \]

  \item Talked about the expectation values of operators
  \[ \mean{\cO} =\frac{1}{\cZ} \int_{-\infty}^{\infty} \mathrm{d}\phi e^{-S(\phi)} \cO(\phi) \]
  also called correlation functions.

  \item Derived the \emph{\textbf{Schwinger-Dyson Equation}} 
  \[ \left\langle \frac{dS}{d\phi} \cO \right\rangle = \left\langle \frac{d\cO}{d\phi}  \right\rangle  \]
\end{itemize}

\begin{dottedbox}
  \emph{Aside:} The Schwinger-Dyson Equation tells us 
  \[ \mean{\frac{\delta S}{\delta \phi(x)} \cO} = \mean{\frac{\delta cO}{\delta \phi(x)}} \]
  
  where $\frac{\delta S}{\delta \phi(x)}$ define the Euler-Lagrange equations of motion:
  \[ \frac{\partial \mathcal{L}}{\partial \phi} - \partial_{\mu} \frac{\partial \mathcal{L}}{\partial \partial_{\mu} \phi } = 0 \]

  \vskip 0.25cm
  Suppose we have point $x$ in space-time and an operator $\cO$ which only depends on some other region which does \emph{not} contain $x$ (eg. $\cO$ could just be the field at a point, in which case the value inside the other region wouldn't depend on $x$, or [insert other examples]).

  \vskip 0.25cm
  [Insert image]

  \vskip 0.25cm
  Then, the Schwinger-Dyson Equation tells us that 
  \begin{align*}
    &\mean{\frac{\delta \cO}{\delta \phi(x)}} = 0 \\ 
    \implies& \mean{\frac{\delta S}{\delta \phi(x)} \cO} = 0
  \end{align*}

  i.e. the \emph{classical} equations of motion are satisfied even in the quantum theory! (as long as there are no other operators acting on $S$ which depend on $\phi(x)$ i.e. no other colliding operators).
  
\end{dottedbox}

\begin{dottedbox}
  \emph{Another Aside:} The way that Symmetries work in QFT is a consequence of the Schwinger-Dyson equation. It extends Noether's Theorem from Classical Mechanics to the \emph{\textbf{Ward-Takahashi Identities}}.

  \vskip 0.5cm
  It's also super useful in studying Non-perturbative theories! And induces the commutation relations! And is responsible for all joy and happiness in the world! The Schwinger-Dyson Equations are great.
\end{dottedbox}

\vskip 0.5cm
[Write stuff related to Adarsh's Question and the ensuing discussion on the correlation function $\mean{m\ddot{x}(t) x(0)}$ for a free field theory with action given by $S = \int_{t_0}^{t_f} \mathrm{d}t \left( \frac{L}{2} m\dot{x}^2 \right) $ -- Couldn't hear well from recording]


\begin{itemize}
  \item For a free theory, the action is very specific - it has to be quadratic in $\phi$. For example, $S = \frac{1}{2}\phi m^ 2\phi $ Then, the Equations of Motion are 
  \[ \frac{dS}{dt} = m^2 \phi \]
  and the Schwinger-Dyson equation says 
  \[ \mean{m^2 \phi \; \cO} = \mean{\frac{d \cO}{dt}} \] or equivalently that 
  \[ \mean{\phi \; \cO} = \frac{1}{m^2} \mean{\frac{d \cO}{dt}} \] 
  So basically, if we have $\phi$ in an expectation value, we can kill it but the price we pay is that we have to replace it with a derivative (w.r.t. $\phi$) and the propagator $\frac{1}{m^2}$.

  \item Last time, we calculated 
  \begin{align*}
    \mean{{\phi \phi}} &= \frac{1}{m^2} \mean{\frac{d}{d\phi} \phi} = \frac{1}{m^2}
  \end{align*}
  This "contraction" is denoted as 
  [include image]

  % Reference: https://www.physicsforums.com/threads/how-to-include-contraction-symbols-in-latex.290341/

  We can think of each of the $\phi$'s as being half-edges and the contraction operation as joining the two half-edges to get a single edge -- which has a \emph{cost} of $\frac{1}{m^2}$.

  \vskip 0.25cm 
  We can also think of the above as $\mean{\phi^2}$ which has slightly different notation. It is represented by two half-edges coming out of the \emph{same} vertex. When we contract them, we get a \emph{closed loop} rather than a single edge.
\end{itemize}

\vskip 0.5cm
Okay, let's calculate $\mean{\phi \phi \phi \phi}$ now.

\begin{align*}
  \mean{\phi \phi \phi \phi} &= \frac{1}{m^2} \mean{\frac{d}{d\phi}\left(\phi \phi \phi\right)} \\
  &= \frac{1}{m^2}\mean{\cdot\;\; \frac{d\phi}{d\phi} \phi \phi} + \frac{1}{m^2}\mean{\cdot\;\; \phi \frac{d\phi}{d\phi}  \phi} + \frac{1}{m^2}\mean{\cdot\;\; \phi \phi \frac{d\phi}{d\phi} }
\end{align*}
where the $\cdot$ just represents the $\phi$ which we killed off and replaced by the $\frac{1}{m^2}$ and derivative. Again, we can write this in Contraction Notation and Diagrammatic Notation as : 

\vskip 0.5cm
Insert figures.

\vskip 0.5cm
Now, we can apply the Schwinger-Dyson equation \emph{again!} i.e. contract again. In terms of contraction notation and diagrammation notation, this would be :

\vskip 0.5cm
Insert figures.

and each of these gives us $\frac{1}{m^4}$, so in total we have 

\[ \mean{\phi \phi \phi \phi} = \frac{3}{m^4} \]

\vskip 0.5cm
If we thought of this as $\mean{\phi^4}$ instead then we would end up with the diagrammatic representation : 

\vskip 0.5cm
Insert figure.

\vskip 0.5cm
\begin{mathdefinitionbox}{}
  What we just did is apply \emph{\textbf{Wick's Lemma}}, which can be expressed in many ways -- such as : 

\begin{itemize}
  \item \[ \boxed{\mean{\phi \cO} = \frac{1}{m^2} \mean{\frac{d\cO}{d\phi}} } \]
  \item \[ \mean{\phi \phi \phi \cdots \phi} = \sum_{\text{all contractions}} \left( \cdots \right)\]
  \item \[ \mean{\cO} = e^{\frac{1}{2}\frac{1}{m^2}\frac{d^2}{d\phi^2}} \restr{\cO}{\phi = 0} \]
\end{itemize}
\end{mathdefinitionbox}

\vskip 0.5cm
All of these are equivalent and contain the same information as the Schwinger-Dyson Equation for a free field theory.

\begin{dottedbox}
  \emph{What's the difference between Wick's Lemma and the Scwinger-Dyson Equation then?} Ask Ivan.
\end{dottedbox}

\begin{dottedbox}
  \emph{How do we interpret the third form of Wick's Lemma?} Let's do an example. Consider the operator $\cO = \phi^2$. Then,

  \begin{align*}
    e^{\frac{1}{2}\frac{1}{m^2}\frac{d^2}{d\phi^2}} \restr{\phi^2}{\phi = 0} &= \left[ 1 + \frac{1}{2} \frac{1}{m^2} \frac{d^2}{d\phi^2} +  \frac{1}{2!} \left( \frac{1}{2}\frac{1}{m^2} \frac{d^2}{d\phi^2} \right)^2 + \cdots \right] \restr{\phi^2}{\phi = 0}  \\ 
  \end{align*}
  \begin{itemize}
    \item But only the first two terms survive since all terms after that contain more than two derivatives and kill off the $\phi^2$.
    \item The first term also gives zero because it gives us $1(\phi^2) = \phi^2$ but we are evaluating this at $\phi = 0$. So, we end up with 
    \[ \mean{\cO} = \frac{1}{m^2} \]
    \item We don't want to differentiate too many times, but if we don't differentiate enough, the terms are killed off. This perfectly represents the contractions: Insert image
    
    The factor of $\frac{1}{2}$ cancels out the symmetry in contractions (we can contract in two different ways: the first onto the second \emph{or} the second onto the first).
  \end{itemize}
\end{dottedbox}

\begin{dottedbox}
  \emph{Exercise:} Verify $\mean{\phi \phi \phi \phi} = \frac{3}{m^4}$ using the third version of Wick's Lemma.
\end{dottedbox}

\vskip 1cm
\subsection{Aside: Is there any topological significance to the shapes of the terms in our Feynman Diagrams?}

\vskip 0.5cm
No; not in the theory we are dealing with. If we're dealing with matrix models, however, we need to put in a little more theory. 

\vskip 0.25cm
If our fields $\phi$ are matrices, then we need to \emph{thicken up} our feynman diagrams. For example, the $\mean{\phi^4}$ diagrams would be 

\vskip 0.25cm
[Insert image]

\vskip 0.25cm
Note that the first two diagrams can be drawn on a sphere while the third cannot -- it must be drawn on a torus. The diagrams now have \emph{genus}, and they are organized by genus. The terms in the expansion will have some \emph{genus coefficient}, and the higher the genus coefficient of a diagram, the higher its genus will be. This is how diagrams in string theory are organized.

\vskip 0.5cm
An example such a theory is \emph{Yang-Mills Theory} which is the theory underlying Quantum Chromodynamics. QCD actually only has 3 colors but something people do to get a good approximation while making calculations easier is to pretend it has $N$ colors and take the $N \rightarrow \infty$ limit. In this limit, the higher genus terms are killed off and only \emph{planar diagram} terms remain.

\vskip 0.5cm
Write about the O(3) model stuff Ivan was mentioning.

\vskip 1cm
\subsection{Interacting Theories}
Let's now move on from \emph{free theories} to \emph{interacting theories}. Suppose we have an interacting $\phi4$ theory whose  action is 
\[ S = \frac{1}{2} \phi m^2 \phi - \frac{\lambda}{4!} \phi^4 \]

where $S_0 = \frac{1}{2}\phi m^2 \phi$ is the \emph{free action}. 

\vskip 1cm
Let's try to calculate the quotient 
\[ \frac{\cZ}{\cZ_0} \]

where 
\[ \cZ = \int_{-\infty}^{\infty} \mathrm{d}\phi e^{-S(\phi)} \] is the partition function of our interacting theory and 
\[ \cZ_0 = \int_{-\infty}^{\infty} \mathrm{d}\phi e^{-S_0(\phi)} = \sqrt{\frac{2\pi}{m^2}}\] is the free partition function.

Then, this ratio is given by 
\begin{align*}
  \frac{\cZ}{\cZ_0} &= \frac{1}{\cZ_0} \int_{-\infty}^{\infty} \mathrm{d}\phi e^{-\frac{1}{2}\phi m^2 \phi} e^{\frac{\lambda}{4!} \phi^4} = \mean{e^{\frac{\lambda}{4!} \phi^4}}_0
\end{align*}
i.e. it is equal to the expectation value of $e^{\frac{\lambda}{4!} \phi^4}$ in the free theory. 

\vskip 0.5cm
This is why we study the ratio! We wanted to study $\cZ$, but we already know $\cZ_0$ and the ratio looks just like an expectation value in the free theory, so we are able to express $\cZ$ immediately as

\[\cZ = \cZ_0 \times  \mean{e^{\frac{\lambda}{4!} \phi^4}}_0  \]

We can then expand the exponential in the expectation value and use linearity to write 

\begin{align*}
  \cZ = \cZ_0 \times \left[\frac{\mean{1}_0}{1} + \frac{\lambda}{4!}\mean{\phi^4}_0 + \frac{1}{2!} \left(\frac{\lambda}{4!}\right)^2 \mean{\phi^4 \phi^4}_0 + \cdots \right]
\end{align*}

This is Perturbation Theory! Let's write this in diagrams now. 

\vskip 0.25cm
Insert Image

\vskip 0.25cm
The three diagrams here are really the same, so we can write the total contribution from the $\frac{\lambda}{4!}\mean{\phi^4}_0$ term as $\lambda \times \frac{1}{8} \times \left(\infty\right)$ where $\infty$ is not infty, but the diagram. The claim is that we could have \emph{guessed} the number $8$. How so? (Brace yourself - this is gonna be cool as HELL)

\vskip 0.5cm
\begin{mathdefinitionbox}{}
  \begin{center}
  $8$ is the \emph{\textbf{number of symmetries of the diagram!}}
  \end{center}
\end{mathdefinitionbox}

Doing this for the other terms too, we have\dots

\vskip 0.5cm
[Insert Diagrams]

\vskip 1cm
\begin{dottedbox}
  \emph{Wait wait wait... how are we defining symmetries of diagrams?} Consider the diagram below.
  
  \vskip 0.25cm
  Insert figure.

  \vskip 0.25cm
  It has a vertix in the center and then four \emph{half-edges} -- rememeber, these four half-edges are the four fields we have contracted together.

  \vskip 0.25cm
  A \emph{symmetry} of the diagram is a mapping of the half-edges into themselves such that 
  \begin{enumerate}
    \item Whenever two half-edges belong to the same vertex \emph{before mapping}, they must still belong to the same vertex after.
    \item Whenever two half-edges form an edge before mapping, they must still form an edge after mapping.
  \end{enumerate}
\end{dottedbox}

\vskip 0.5cm
A cool consequence of this is that a mathematician trying to compute the number of symmetries of some graph might just be able to get the job done by hiring their physicist friend to compute the correlation function of some appropriate field theory! Because, at the end of the day, 
\[ \frac{\cZ}{\cZ_0} = \sum_{\substack{\text{All diagrams } \Gamma \\ \text{with 4 valent vertices}}} \frac{w(\Gamma)}{\left| \text{Aut}(\Gamma) \right|} \]

where $w(\Gamma)$ is a weightage, given by the Feynman Rules, equal to the propagator.

\vskip 0.5cm
\begin{dottedbox}
  \emph{Exercise:} Compute 
  \[ \frac{\cZ}{\cZ_0} = \mean{e^{\frac{g}{3!} \phi^3}}_0 = \cdots + \cO(\phi^6) \]
  i.e. compute the perturbations up to the 6th order in $\phi$, using the third version of Wick's Lemma 
\end{dottedbox}

\end{document}
