\documentclass[11pt]{article}

% basic packages
\usepackage[margin=1in]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{custom}
\usepackage{lipsum}

\usepackage{xcolor}
\usepackage{tikz}

\usepackage[most]{tcolorbox}
\usepackage{xcolor}
\usepackage{mdframed}

% page formatting
\usepackage{fancyhdr}
\pagestyle{fancy}

\renewcommand{\sectionmark}[1]{\markright{\textsf{\arabic{section}. #1}}}
\renewcommand{\subsectionmark}[1]{}
\lhead{\textbf{\thepage} \ \ \nouppercase{\rightmark}}
\chead{}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{}
\setlength{\headheight}{14pt}

\linespread{1.03} % give a little extra room
\setlength{\parindent}{0.2in} % reduce paragraph indent a bit
\setcounter{secnumdepth}{2} % no numbered subsubsections
\setcounter{tocdepth}{2} % no subsubsections in ToC


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CUSTOM BOXES AND STUFF
\newtcolorbox{redbox}{colback=red!5!white,colframe=red!75!black}
\newtcolorbox{bluebox}{colback=blue!5!white,colframe=blue!75!black}

\definecolor{lightblue}{RGB}{173,216,230} % Light blue color
\definecolor{darkblue}{RGB}{0,0,139} % Dark blue color

% Define the custom proof environment
\newtcolorbox{ex}[2][Example]{
  colback=red!5!white, % Light blue background
  colframe=red!75!black, % Darker blue border
  coltitle=white, % Title color
  fonttitle=\bfseries, % Title font style
  title={{#2}},
  arc=1mm, % Rounded corners with 4mm radius,
  boxrule=0.5mm,
  left=2mm, right=2mm, top=2mm, bottom=2mm, % Padding inside the box
  breakable, % Allow box to be broken across pages
  before=\vspace{10pt}, % Padding above the box
  after=\vspace{10pt}, % Padding below the box
  before upper={\parindent15pt} % Ensure indentation
}

% Define the custom proof environment
\newtcolorbox{defn}[2][Definition]{
  colback=green!5!white, % Light blue background
  colframe=green!75!black, % Darker blue border
  coltitle=white, % Title color
  fonttitle=\bfseries, % Title font style
  title={{#2}},
  arc=1mm, % Rounded corners with 4mm radius,
  boxrule=0.5mm,
  left=2mm, right=2mm, top=2mm, bottom=2mm, % Padding inside the box
  breakable, % Allow box to be broken across pages
  before=\vspace{10pt}, % Padding above the box
  after=\vspace{10pt}, % Padding below the box
  before upper={\parindent15pt} % Ensure indentation
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% make title page
\thispagestyle{empty}
\bigskip \
\vspace{0.1cm}

\begin{center}
{\fontsize{22}{22} \selectfont PSI QFT I}
\vskip 16pt
{\fontsize{36}{36} \selectfont \bf \sffamily Notes}
\vskip 24pt
{\fontsize{18}{18} \selectfont \rmfamily Keshav Balwant Deoskar} 
\vskip 6pt
{\fontsize{14}{14} \selectfont \ttfamily kdeoskar@berkeley.edu} 
\vskip 24pt
\end{center}

% {\parindent0pt \baselineskip=15.5pt \lipsum[1-4]} 

% make table of contents
% \newpage



\vskip 0.5cm
This template is based heavily off of the one produced by \href{https://knzhou.github.io/}{Kevin Zhou}.

% \microtoc
\tableofcontents 

% main 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Lie Groups}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 0.5cm
In physics, we can learn a great deal from studying the symmetries of \emph{continuous} systems. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Representations of Lie Groups and Lie Algebras}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{What is a Representation?}
\begin{itemize}
    \item To understand what a group really \emph{is}, it can be very enlightening to study what the group \emph{does} i.e. to study \emph{\textbf{group actions}}. Further, linear algebra is easier than abstract algebra, so if we can study the action of a group in terms of linear algebraic objects, we'll get a lot more mileage.
    \item How exactly do we do this? We can use some sort of map to assign a \emph{linear operator} over that vector space to each group element to describe (or represent) the action of each group element on the vector space elements. The map that we use is a \textbf{representation} of the group.
\end{itemize}

\vskip 0.5cm
\begin{redbox}
  Recall that the space of all linear operators $\rho \text{ : } V \rightarrow V$ is denoted $\homend{V}$. The subset of these operators which are invertible (isomorphisms on $V$) is denoted $\aut{V}$. 
  
  \vskip 0.5cm
  Notably, $\aut{V}$ has a group structure! \begin{thought}{Check this!} \end{thought} On the other hand, $\homend{V}$ becomes an (Associative, and later Lie) Algebra if we define the commutator for $A, B \in \homend{V}$ as
  \[ [A, B] = AB - BA \] 
  
  % \begin{thought}{Check this!} \end{thought}
\end{redbox}

\vskip 0.5cm
Now the formal definition.

\vskip 0.5cm
\begin{definition}{Group Representation}
  Given a group $G$ and vector space $V$, a group homomorphism \[ \rho \text{ : } G \rightarrow \mathrm{Aut}(V) \] is called a \textbf{representation} of $G$ in $V$.
\end{definition}

\begin{example}
  Complete this later
\end{example}

\vskip 0.5cm

We can use the same idea to define the representation of an algebra, but this time with $\homend{V}$.

\begin{definition}{Lie Algebra Representation}
  Given a Lie algebra $\mathcal{G}$ and vector space $V$, an algebra homomorphism \[ \rho' \text{ : } \mathcal{G} \rightarrow \homend{V} \] is called a representation of the Lie algebra $\mathcal{G}$ over $V$.
\end{definition}

\begin{remark}{The representations $\rho$ and $\rho'$ of a lie group and its lie algebra are related! so $\rho'$ is called the \textbf{derived representation}.}
\end{remark}

\begin{ex}{Fecko, Exercise 12.1.4}
    Consider a Lie algebra $\mathcal{G}$ whose basis elements $\{E_i\}$ satisfy the commutation relations 
    \[ [E_i, E_j] = c^k_{ij} E_k  \]
    and a representation $f \tcolon \mathcal{G} \rightarrow \homend{V}$. Then, define $\mathcal{E}_i \equiv f(E_i)$. Since $f$ is a homomorphisms between algebra, it is linear and respects the commutator i.e. for $A, B \in \mathcal{G}$
    \[ f\left( [A, B] \right) = \left[f(A), f(B)\right] \] 

    Thus, 
    \begin{align*}
      \left[ \mathcal{E}_i, \mathcal{E}_j \right] &= \left[f(E_i), f(E_j) \right] \\
      &= f\left([E_i, E_j]\right) \\
      &= f\left(c^k_{ij} E_k\right) \\
      &= c^{k}_{ij} f(E_k) \\
      &= c^{k}_{ij} \mathcal{E}_k 
    \end{align*}

    \begin{thought}{The basis elements of the representation satisfy the same commutation relation as those of the Lie Algebra!}
    \end{thought}
\end{ex}

\begin{ex}{Fecko, Exercise 12.1.5}
    Do this one later
\end{ex}

\vskip 0.5cm
\begin{itemize}
  \item The assignment from Lie Group to Lie Algebra $G \mapsto \mathcal{G}$ is nice and unique, but the other way around can get messy.
  \item Similarly, given a Lie group representation $\rho$ there is a unique Lie algebra represenation $\rho'$, but not necessarily the other way around. 
\end{itemize}


\begin{ex}{Fecko, Exercise 12.1.6}
  \begin{enumerate}[label=(\roman*)]
    \item Consider the Lie Group $H = \aut{V} \equiv \mathrm{GL}(V)$. 
    Recall that the Lie Algebra of $H$ is 
  \end{enumerate}
\end{ex}

\vskip 0.5cm
Write about $\rho$-invariant inner products.

\vskip 1cm
\subsection{Reducible and Irreducible Representations}




\vskip 1cm
\subsection*{References for the chapter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%







% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newpage
% \section*{Chapter name}

% \vskip 1cm
% \subsection*{References for the chapter}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}









